The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-08-05 ApJ/table1.tex
Reworked enrichment fraction table.

\begin{deluxetable*}{ccccccc}
%\tablecolumns{7}
\tabletypesize{}
\tablewidth{0pc}
\tablecaption{Enrichment Fractions\label{tab:enrich}}

\tablehead{\colhead{Source} & \colhead{Weighting} & 
  \multicolumn{5}{c}{Metallicity Cut (in units of [Z/H])} \\
%%%%%%%%%%
  \cline{3-7} \\
%%%%%%%%%%
  \colhead{} & \colhead{} & 
  \colhead{-6} & \colhead{-5} & \colhead{-4} & \colhead{-3} & \colhead{-2}
}
\startdata
Pop III & Volume & 0.0384 & 0.0331 & 0.0268 & 0.0188 & 0.00836 \\
Pop III & Mass & 0.144 & 0.125 & 0.102 & 0.0650 & 0.0124 \\
Pop II & Volume & 0.00560 & 0.00397 & 0.00236 & 0.00102 & 0.000266 \\
Pop II & Mass & 0.0525 & 0.0438 & 0.0344 & 0.0251 & 0.0174
\enddata
\end{deluxetable*}

>>>>

\begin{deluxetable}{ccccc}
%\tablecolumns{7}
\tabletypesize{}
\tablewidth{\columnwidth}
\tablecaption{Enrichment Fractions\label{tab:enrich}}

\tablehead{\colhead{[Z/H]} & 
  \colhead{$f_v$(Pop III)} & \colhead{$f_m$(Pop III)} & 
  \colhead{$f_v$(Pop II)} & \colhead{$f_m$(Pop II)}
}
\startdata
-6 & 3.84(-2) & 1.44(-1) & 5.60(-2) & 5.25(-2) \\
-5 & 3.31(-2) & 1.25(-1) & 3.97(-2) & 4.38(-2) \\
-4 & 2.68(-2) & 1.02(-1) & 2.36(-2) & 3.44(-2) \\
-3 & 1.88(-2) & 6.50(-2) & 1.02(-2) & 2.51(-2) \\
-2 & 8.36(-3) & 1.24(-2) & 2.66(-3) & 1.74(-2)
\enddata

\tablecomments{$f_v$ and $f_m$ are volume filling and mass-weighted
  fractions, respectively, above several different metallicity cuts.
  Values are listed in scientific notation with the exponents in
  parentheses.}

\end{deluxetable}
